### 2022-09-28 main/chapter_context.tex
begin sketching susy section

Fine-tuning criteria dislike tight constraints, and naturalness contains
various ideas of which one is that nice numbers should have moderate orders of
magnitude~\cite{giudice2008naturally}.
For example, $\theta_\mathrm{CP}$ is unattractively fine-tuned within its
experimental constraint of $\theta_\mathrm{CP} \lesssim 10^{-11}$, and that
large $11$ in its exponent defies naturalness.

Another example is the hierarchy problem of the Higgs boson mass $m(h)$,
which notes that the energy scale of new heavy particles linearly modifies the
$m(h)$ through direct or indirect couplings.
With any particles near the Planck scale $\sim 10^{18}\,\eV[G]$, implementing
the observed $m(h) \sim 10^{2}\,\eV[G]$ therefore requires finely-tuned
cancellations between positive and negative additions.
New fermions subtract from $m(h)$ and new scalars add by similar amounts,
so new models can implement this fine-tuning by inserting only matched pairs of
fermions and scalars --- this is the strategy of supersymmetric models.

@@

@@

\subsubsection{Minimal supersymmetric models}
Lightest Supersymmetric Particle (LSP)

\subsubsection{Guage Mediated Supersymmetry Breaking}
Gauge Mediated Supersymmetry Breaking (GMSB)

>>>>

Fine-tuning criteria dislike tight constraints, and naturalness contains
various ideas of which one is that nice numbers should have moderate orders of
magnitude~\cite{giudice2008naturally}.
For example, $\theta_\mathrm{CP}$ is unattractively fine-tuned by an
observation of $\theta_\mathrm{CP} \lesssim 10^{-11}$, and that
large $11$ in its exponent also defies naturalness.

Another example is the hierarchy problem of the Higgs boson mass $m(h)$,
which notes that the energy scale of new heavy particles add quadratically to
$m(h)^2$ through direct or indirect couplings.
With any particles near the Planck scale $\sim 10^{18}\,\eV[G]$, implementing
the observed $m(h) \sim 10^{2}\,\eV[G]$ therefore requires finely-tuned
cancellations between positive and negative additions.
New fermions subtract from $m(h)$ and new scalars add by similar amounts,
so new models can implement this fine-tuning by inserting only matched pairs of
fermions and scalars --- this is the strategy of supersymmetric models.

@@

% supersymmetry

% supersymmetric models

% fermion boson multiplets

% table of particle content

% explain mixing

% reproduce arguments for Wino-Bino C1 N2

Lightest Supersymmetric Particle (LSP)

Gauge Mediated Supersymmetry Breaking (GMSB)

% reproduce arguments for goldsino and gravitino
% spin-$3/2$ parts couples only gravitationally, see another spin-$1/2$ fermion

@@
